--- 
title: "Travaux Pratiques de Biométrie 3"
author: "Benoît Simon-Bouhet"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    highlight: kate
    config:
      edit: null
      sharing:
        twitter: no
        facebook: no
        github: yes
        all: no
      toc:
        collapse: subsection
  bookdown::pdf_book:
    citation_package: natbib
url: 'https\://besibo.github.io/Biometrie3/'
github-repo: "besibo/Biometrie3"
bibliography: [book.bib, packages.bib]
biblio-style: apalike
papersize: a4paper
geometry: "left=3.75cm, right=3.75cm, top=3cm, bottom=3cm"
link-citations: yes
urlcolor: "blue"
description: "Ce livre est un document permettant de réaliser des analyses statistiques descriptives, des tests d'hypothèse, des régressions linéaires et des analyses de variances dans le cadre des travaux pratiques de Biométrie 3."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.


```{r package_bibliography, include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'tidyverse', 'ggplot2', 'gridExtra'
), 'packages.bib')
```


```{r setup, include=FALSE, cache=FALSE, results=FALSE, message=FALSE}
options(replace.assign = TRUE, width = 70)
options(repos = "http://cran.r-project.org/")

list.of.packages <- c("nycflights13", "gapminder", "knitr", "tidyverse", "gridExtra", "devtools", "extrafont", "kableExtra")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

library(devtools)
library(knitr)
library(tidyverse)

if( !("EDAWR" %in% installed.packages()[,"Package"]) ) {
  install_github("rstudio/EDAWR")
}

opts_chunk$set(fig.path = 'figure/', cache.path = 'cache/', tidy = TRUE,
               fig.align = 'center', out.width = '90%', fig.asp = 0.618,
               fig.show = 'hold', fig.pos = 'htpb', par = TRUE, comment = NA, cache = TRUE)
```



<!-- Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab). -->

<!-- You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015]. -->
